---
title: "Git and GitHub for Collaboration"
author: "Vitor Borges-Júnior"
date: "10/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Step 1 - Create a new repository




# Step 2 - Create a new Version Control RStudio Project

# Step 3 - First commit and push request

# Step 4 - Inviting a collaborator

- Invite a collaborator from the GitHub page

- Ask for the collaborator accept the invitation

- Ask for the colaborator to make some modification in the file

# Step 5 - First pull rerquest

- Ask the collaborator to make changes in the file

- Ask the collaborator to commit changes

- Ask the collaborator to make a push request

- Do a pull request yourself

# Step 6 - Solving merge conflict

# Step 7 - Barnching

- Create a new branch

- Ask your colaborator to make changes and push them

- Do a pull request and merge the branch with changes with the main branch

```{r}
library(usethis)
create_from_github("llendway/pr_practice", fork = TRUE)
create_github_token("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")
```

